\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\title{Organ-Age: A Multimodal Fusion of Transcriptomic and Radiological Signals for Organ-Resolved Biological Age Estimation}
\author{
  Arnav Sangle \\
  Independent Researcher, Ranchview High School, Irving TX, USA \\
  \texttt{arnavsangle08@gmail.com}
}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Biological aging does not proceed uniformly across the body. Different organs accumulate
molecular, structural, and physiological damage at different rates, yet most biological age
predictors rely on a single data type and consequently collapse aging into a single,
organism-wide estimate. This compression limits clinical interpretability and obscures organ-level
trajectories that span both gene regulation and tissue morphology.

Here I present Organ-Age, a framework that estimates organ-resolved biological age by fusing
transcriptomic and radiological signals. Using bulk RNA-seq from GTEx, chest radiographs from
CheXpert, and structural brain MRI from IXI, the model first encodes each modality into a
fixed-length embedding, aligns embeddings into a shared latent space via an InfoNCE-style
contrastive objective, and then merges them through a transformer-based fusion module to
produce organ-level age predictions with uncertainty. On a combined cohort of over 190,000
samples, the aligned multimodal model achieves a mean absolute error of $\sim$9.3 years and
tracks chronological age closely across the adult lifespan.

Residual deviations between predicted organ age and chronological age---organ-age deltas---expose
structured acceleration and deceleration patterns that differ by organ and are consistent with
known tissue-level biology. These findings suggest that biological age is better modeled as a
multi-signal, organ-resolved construct than as a single number and that alignment plus attention-based
fusion is a viable route toward interpretable organ-specific aging assessment.
\end{abstract}

\vspace{1em}
\noindent\textbf{Keywords:} biological age, organ aging, multimodal learning, contrastive alignment, transcriptomics, fusion transformer, interpretability

\end{document}
